**Density Dependence**

### 2023-02-20 Rmd/mseMac.Rmd
1st

---
title: "**Density Dependence**"
subtitle: "MSE for Mackerel"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE
tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
bibliography: refs.bib
---

>>>>

---
title: "**Density Dependence**"
subtitle: "MSE for Mackerel"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
mathjax: TRUE
tags: FLR FLCore introduction
license: Creative Commons Attribution-ShareAlike 4.0 International Public License
bibliography: refs.bib
---
